
	\documentclass{leresume}
	\usepackage{lelists}
	\setlength{\listtopsep}{0pt}
	\setlength{\leftlistindent}{0pt}
	\setlength{\listlevelleftindent}{12pt}
	\setlength{\rightlistindent}{0pt}


	\usepackage{lesubscripts}
	\usepackage{lehyperlink}
	\usepackage{leheadersandfooters}

	\usepackage{multicol}
	\setlength{\premulticols}{0in}
	\setlength{\postmulticols}{0in}

	\usepackage{leaddress}
	\usepackage{times}

	\usepackage[resetlabels]{multibib}
	\newcites{publications}{Publications}
	\newcites{patents}{Patents}

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% DEFINE PERSONAL INFORMATION.  DEFINE BEFORE BEGIN DOCUMENT OR IT
	% WILL NOT BE PROCESSED CORRECTLY.
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\titlename{Lance A. Endres, Ph.D.}
	\addresslinea{\myaddresslineoneshort}
	\addresslineb{\myaddresslinetwo}

	\renewcommand*{\phonename}{{\small{}Phone:}}
	\phone{\myphoneone}
	\renewcommand*{\emailname}{{\small{}Email:}}
	\email{\myemailone}
	\website{\mywebsiteoneshort}
	\websitetwo{\mywebsitetwoshort}
	
	% Prevent indented paragraphs.
	\setlength{\parindent}{0pt}

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% BEGIN DOCUMENT.
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\pagestyle{lehorizontallinewpagenumber}
	\begin{document}
	\thispagestyle{leempty}
	\makeresumeheaderC

	\catagory{Summary}
	Experienced project manager, team leader, and researcher with a strong background working with international teams and a proven ability to creatively solve complex problems. Areas of expertise:
	\vspace{-6pt}
	\begin{multicols}{3}
		\begin{bulletedlist}
			
			\item Machine Learning
			\item Artificial Intelligence
			\item Computational Mechanics
			\item Computational Dynamics
			\item Data Science
			\item Software Development
			\item Software Architecture
			\item Research
			\item Project Management
			\item Team Leading
			\item Drilling Dynamics
			\item Drilling Mechanics
		\end{bulletedlist}
		\end{multicols}

	
		\catagory{Work Experience}
		
            \catentry{12/2024 - Current}
            {Manager for Digital, Automation, and Interpretation}
            {CNPC USA}
			{Houston, TX}
			Team Manager for Digital, Automation, and Interpretation
		\begin{bulletedlist}
			
		\item
		
				Conducted regular performance reviews and coaching sessions.
			
		\item
		
				Facilitated conflict resolution and team-building activities to foster a collaborative work culture.
			
		\item
		
				Collaborated with senior leadership to align team objectives with strategic business goals.
			
		\item
		
				Managed resource planning, project delegation, and training initiatives.
			
		\item
		
				Reported on key metrics, project status, and risks to stakeholders in monthly progress meetings.
			
		\end{bulletedlist}
	
            \catentry{9/2022 - 12/2024}
            {Senior Research Engineer}
            {CNPC USA}
			{Houston, TX}
			Project leader for developing physics and data based prediction software.
		\begin{bulletedlist}
			
		\item
		
				Leveraged industry contacts to secure software licenses and access open-source solutions, accelerating the modeling program by five years and a cost savings of \$1MM.
			
		\item
		
				Designed and developed a generalized Python library to analyze and plot high frequency time-series data.  The library includes signal processing algorithms, 
				finite precision arithmetic mathematics, and automatic units handling. By design, the data plotting is separated from plot formatting.  Saves 70-95\% of code writing when analyzing and plotting data.
			
		\item
		
				Designed LLM prompts to summarize large documents and extract structured content from document collections.  Achieved a 95\% reduction in data summarization and report writing time.
			
		\item
		
				Managed software projects utilizing in-house and third party resources.
			
		\item
		
				Mentored and guided software developers and researchers.
			
		\end{bulletedlist}
	
            \catentry{3/2021 - 9/2022}
            {Founder and President}
            {Ikosy Technologies}
			{Spring, TX}
			Founded Ikosy Technologies to create easy-to-use desktop pick-and-place technology.
		\begin{bulletedlist}
			
		\item
		
				Identified a unique business opportunity leading to the development of a comprehensive business plan.
			
		\item
		
				Designed a desktop-sized pick-and-place machine that uses G-code to assemble electronics.
			
		\item
		
				Recruited and led a team of founders.
			
		\end{bulletedlist}
	
            \catentry{1/2014 - 6/2020}
            {Principal Engineer}
            {APS Technology}
			{Houston, TX}
			Developed engineering software, performed data and drilling dynamics analysis.\nolinebreak[4]
		\begin{bulletedlist}
			
		\item
		
				Developed FEA-based software for structural analysis of drill strings, calculating deflections, stresses, natural frequencies, and mode shapes to assess bending capabilities and stress limits.
			
		\item
		
				Developed a software application used to automate the cleaning and processing of data.  The software uses specialized data processing techniques 
				and algorithms to automatically separate the data into drilling versus non-drilling time.  It reduced the data processing time by 97\%.
			
		\end{bulletedlist}
	
            \catentry{1/2006 - 11/2013}
            {Researcher in Drilling Mechanics and Dynamics}
            {Baker Hughes}
			{The Woodlands, TX}
			
			Conducted research in drilling mechanics and dynamics.
		
		\begin{bulletedlist}
			
		\item
		
				Developed a computer model used to predict the dynamic behavior of drill bits.
				
		\begin{bulletedlist}
			
		\item
		
						Written in C++, the model uses a hybrid physics and data driven approach to predict behavior.  In this approach, the known physics are captured by physical models.  The unknown physics are modeled using machine learning techniques.
					
		\item
		
						Oversaw the physics models, software design and architecture, and project management, ensuring software accuracy, timely deliverables, and adherence to budget, resulting in efficient project execution.
					
		\item
		
						Developed a technique to reduce the cost of model fitting by an order of magnitude.
					
		\item
		Transferred development to an overseas-based software team and managed them.
		\end{bulletedlist}
	
		\item
		
				Conducted research that led to an improved theoretical understanding of lateral drill bit vibrations and which I used to develop novel techniques for
				designing drill bits. 
		\textit{This let engineers design bits directly rather than randomly searching for a solution.}
	
		\item
		Developed a technique used to interpret laboratory data.  The technique is a physics-based approach that replaced the previous assumption-based method.
		\end{bulletedlist}
	
		\catagory{Projects}
		
		\project{Designing Generative AI Solutions with Azure Open AI Sentiment Analysis}{
		Train an LLM to analyze user-generated reviews to identify customer demands and opportunities.
	}{
			LLM, OpenAI, Azure, prompt engineering, single shot prompt, multi shot prompt
		}
		
		\project{Leveraging Generative AI for Business Applications Product Review Sentiment Analysis}{
		Use generative AI (LLM) to take unstructured customer reviews as input and return structured responses that can be used to take action to optimize customer experiences.
	}{
			LLM, OpenAI, Azure, Prompt Engineering
		}
		
		\project{Twitter Sentiment Analysis for Airline Services}{
		Identify the sentiments of tweets to understand the customer satisfaction for an airline.
	}{
			NLP, count vectorizer, TF-IDF vectorizer, TensorFlow, word embedding, LSTM, VADER
		}
		
		\project{Plants Seedling Image Classification}{
		Classify plant species based on images of the seedlings using a Convolutional Neural Network.
	}{
			convolutional neural network, TensorFlow, Keras, Google Colab, Python
		}
		
		\project{Bank Customer Churn Prediction}{
		Identify the customers that are more likely to churn by building an Artificial Neural Network.
		}{
			artificial neural network, TensorFlow, Keras, Google Colab, Python
		}
		

    \catagory{Publications}
    
        \nocitepublications{ref:endres2003a}
    
        \nocitepublications{ref:endres2004a}
    
        \nocitepublications{ref:krysl2005a}
    
        \nocitepublications{ref:endres2007a}
    
        \nocitepublications{ref:endres2007bshort}
    
        \nocitepublications{ref:schwefe2014a}
    
        \nocitepublications{ref:endres2015a}
    
        \nocitepublications{ref:yoon2024a}
    
        \nocitepublications{ref:mahjoub2025a}
    
	\bibliographystylepublications{leplain}
	\bibliographypublications{strings, le}
	
	\catagory{Patents}
	
        \nocitepatents{ref:endres2013a}
    
        \nocitepatents{ref:endres2013b}
    
        \nocitepatents{ref:prevost2013a}
    
        \nocitepatents{ref:hohl2015a}
    
	\bibliographystylepatents{leplain}
	\bibliographypatents{strings, le}

    \catagory{Skill Set}
    \begin{bulletedlist}
		
		\item \textbf{Machine Learning, Artificial Intelligence, and Data Science}: ANNs,
                        CNNs,
                        NLP,
                        TensorFlow,
                        data analysis,
                        data cleaning,
                        algorithm design,
                        scikit-learn,
                        pandas,
                        numpy,
                        Matplotlib,
                        Seaborn,
                        XGBoost,
                        hypothesis testing,
                        confidence interval,
                        Decision Trees,
                        Random Forest,
                        k-nearest neighbors,
                        k-means clustering,
                        linear regression,
                        logistic regression,
                        time series data,
                        supervised learning,
                        unsupervised learning,
                        clustering,
                        PIL,
                        and OpenCV.
                        
		\item \textbf{Software Development}: software architecture,
                        quality control,
                        unit testing,
                        system checks,
                        documentation,
                        customer interaction,
                        C,
                        C++,
                        C\#,
                        Python,
                        .NET,
                        MAUI,
                        Visual Basic,
                        Fortran,
                        AutoLISP,
                        multithreading,
                        XML,
                        XPath,
                        XSLT,
                        HTML,
                        XHTML,
                        CSS,
                        QT,
                        UML,
                        XML Schemas,
                        OpenGL,
                        JavaScript,
                        profiling,
                        optimization,
                        and code review.
                        
		\item \textbf{Software}: Visual Studio,
                        Matlab,
                        Spyder,
                        Jupyter Notebooks,
                        Google Colab,
                        AutoCAD,
                        GitHub,
                        LaTeX,
                        Fusion 360,
                        Solidworks,
                        KiCad,
                        Photoshop,
                        SVN,
                        CVS,
                        Ansys,
                        and MS Project.
                        
		\item \textbf{Research and Engineering}: design of laboratory experiments,
                        stability analysis,
                        signal processing,
                        FEA,
                        CFD (basic),
                        plasticity,
                        and structural engineering.
                        
		\item \textbf{Other}: 3D modeling,
                        3D printing,
                        computer trouble shooting and repair (hardware and software),
                        basic electronics \& circuits,
                        PCB design,
                        microprocessor basics,
                        Arduino and Raspberry Pi,
                        embedded programming (Arduino),
                        soldering,
                        and surface mount devices and reflowing.
                        
	\end{bulletedlist}

	\catagory{Continuing Education}
	
            \catentryeducation{2024}
                {Post Graduate Program in Generative AI and LLMs for Business with Microsoft Azure}
                {Great Learning}
		
            \catentryeducation{2023}
                {Certificate in Project Management}
                {University of Houston}
		
            \catentryeducation{2022}
                {Post Graduate Program in Artificial Intelligence and Machine Learning}
                {University of Texas}
		

	\catagory{Education}
	
            \catentryeducation{2007}
                {Ph.D. in Structural Engineering}
                {University of California, San Diego}
		
            \catentryeducation{2004}
                {M.S. in Structural Engineering}
                {University of California, San Diego}
		
            \catentryeducation{1999}
                {B.S. in Civil Engineering}
                {Lawrence Technological University}
		

    \end{document}
    