
    \documentclass{resume}
    \usepackage{lelists}
    \setlength{\listtopsep}{0pt}
    \setlength{\listindent}{0pt}

    \usepackage{subscripts}
    \usepackage{lehyperlink}
    \usepackage{leheadersandfooters}

    \usepackage{multicol}
    \setlength{\premulticols}{0in}
    \setlength{\postmulticols}{0in}

    \usepackage{leaddress}
    \usepackage{times}
	
	\usepackage[resetlabels]{multibib}
	\newcites{publications}{Publications}
	\newcites{patents}{Patents}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DEFINE PERSONAL INFORMATION.  DEFINE BEFORE BEGIN DOCUMENT OR IT
% WILL NOT BE PROCESSED CORRECTLY.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \name{Lance A. Endres, Ph.D.}
	\addresslinea{\myaddresslineoneshort}
	\addresslineb{\myaddresslinetwo}

	\renewcommand*{\phonename}{{\small{}Phone:}}
	\phone{\myphoneone}
	\renewcommand*{\emailname}{{\small{}Email:}}
	\email{\myemailthree}
	\website{\mywebsiteone}

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% BEGIN DOCUMENT.
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\pagestyle{lehorizontallinewpagenumber}
	\begin{document}
	\thispagestyle{lefooterhorizontalline}
	\makeresumeheaderB

	\catagory{Summary}
	An experienced research and development engineer in the area of computational dynamics and mechanics. Creative thinker with excellent presentation and communication skills. Experience with project management, team leading, and working internationally on team based projects.

	\catagory{Areas of Expertise}
	Computational Mechanics $\bullet$ Computational Dynamics $\bullet$ Numerical Integration $\bullet$ Dynamics of Drill Bits $\bullet$ Cutter-Rock Interaction $\bullet$ BHA Dynamics $\bullet$ Data Analysis and Interpretation $\bullet$ Whirl $\bullet$ Software Development $\bullet$ Software Architecture $\bullet$ Programming $\bullet$ Research $\bullet$ Teaching $\bullet$ Technical Writing

    \catagory{Experience}
    
            \catentry{1/2014 - Current}
            {Principal Engineer}
            {APS Technology}
			{Houston, TX}
			
					\vspace*{-6pt}
					\noindent Worked in the area of drilling dynamics, drilling optimization, and data processing and analysis.
		\begin{bulletedlist}
			
		\item 
					Developed data processing techniques and algorithms.  Implemented as a software package used to automate cleaning and processing of
					drilling data.  UI is written in C\#.  The primary algorithm is a C library with both C++ and C\# wrappers.
				
		\item 
					Worked on BHA analysis software to fix software issues and assess and repair sciencetific issues.  Analyzed a prototype version
					written in Visual Basic to evaluate it's abilities.  Currently rewriting the software in C\# to fix both a poor software design
					and remove or repair any scientfic areas that need improving.
				
		\item 
					Developed generalized plotting software, written in C\#, which is designed to work with data from any downhole tool.  Software
					needed to be immune to changes in firmware, easily adapt to new tool output, and handle errors resulting from corrupted data.
					The software consistded of a data translation and validation library (custom written) combined with INT's WellLog plotting library.
				
		\item 
					Provided recommendations on developing a path to full drilling automation.  Contributions included assessing available resources, assessing currently available technology, and determining what technology needs to be developed.
				
		\item 
					Developed an architecture for all of the drilling optimization and automation software.
				
		\item 
					Taught drilling dynamics and mechanics, object oriented design practices, and .Net Framework.
				
		\end{bulletedlist}
			\vspace*{-12pt}
	\hspace*{0pt}\\ \vspace*{-2pt}
				
            \catentry{1/2006 - 11/2013}
            {Researcher in Drilling Mechanics and Dynamics}
            {Baker Hughes}
			{Houston, TX}
			
					\vspace*{-6pt}
					\noindent 
				Conducted research in the areas of drilling mechanics and dynamics.  Work included developing theoretical understandings of drilling behavior, designing laboratory experiments, and developing computer models to predict drilling behavior.
			
		\begin{bulletedlist}
			
		\item 
					Developed an advanced, proprietary computational dynamics application used to predict and analyze the dynamic behavior of drill bits,
					forces acting on cutters, cutting/bottom hole patterns, and AKO kinematics.  Was responsible for software design and architecture,
					algorithms, implementation and accuracy of physics, project schedule, deliverables, and budget.  Software was primarily written in C++.
				
		\item Interviewed, selected, and lead a team based in Russia to continue the development of the software used to analyze drill bit dynamics.  The long term goal was to train this team to take over the project.  Organized aditional trainings and presentations for the Siberian based team.  Training took place both remotely and in person.
		\item Served as team member on project with the objective to advance understanding of torsional and lateral drilling dynamics through a series of computer, laboratory, and full scale drill rig experiments.
		\item Developed a laboratory analysis technique to improve understanding of lateral bit dynamics and more precisely define backward whirl.
		\item Developed new techniques for designing drill bits to prevent lateral vibrations both in the new and worn states.
		\item Designed and oversaw running of experiments in laboratory setting and on a full scale drill rig.
		\item Analyzed and interpreted computer, laboratory, and drill rig data.
		\item 
					Developed software to post process a variety of disjointed laboratory and computer data types in a standardized, uniform
					way.  Software was built in two pieces, a C\# ''translator'' and a large collection of Matlab utities and classes which read
					the translator output, then processed and displayed the data.
				
		\item Trained new employees and directed the work of interns.
		\item Served as a member of a cross-divisional numerical modeling and simulation committee.
		\end{bulletedlist}
			\vspace*{-12pt}
	\hspace*{0pt}\\ \vspace*{-2pt}
				
            \catentry{9/2002 - 12/2005}
            {Graduate Student Researcher}
            {University of California, San Diego}
			{La Jolla, CA}
			
					\vspace*{-6pt}
					\noindent 
				Performed research in the area of computational mechanics and numerical integration.  Research was implemented
				primarily in C, C++, C\#, and Matlab.
			\hspace*{0pt}\\ \vspace*{-2pt}
				
            \catentry{9/2001 - 6/2002}
            {Teaching Assistant}
            {University of California, San Diego}
			{La Jolla, CA}
			
					\vspace*{-6pt}
					\noindent 
				Wrote exams, graded homework and exams, held office hours, and lectured classes when the professor
				was unavailable.  Specifically requested by several students to be their T.A.\ because of
				performance as their T.A.\ in a prior class.
			\hspace*{0pt}\\ \vspace*{-2pt}
				
            \catentry{11/1998 - 9/2000}
            {C.A.D. Manager}
            {Strategic Energy Solutions}
			{Ferndale, MI}
			
					\vspace*{-6pt}
					\noindent 
				Created high quality, professional engineering drawings in AutoCAD.  Conducted training, established
				and maintained C.A.D. standards, and wrote productivity software for AutoCAD.
			\hspace*{0pt}\\ \vspace*{-2pt}
				
		\vspace*{-8pt}
	

	\catagory{Education}
	
            \catentryeducation{2007}
                {Ph.D. in Structural Engineering}
                {University of California, San Diego}
		
            \catentryeducation{2004}
                {M.S. in Structural Engineering}
                {University of California, San Diego}
		
            \catentryeducation{1999}
                {B.S. in Civil Engineering}
                {Lawrence Technological University}
		

    \vspace*{1pt}
    \catagory{Publications}
    
        \nocitepublications{ref:endres2003a}
    
        \nocitepublications{ref:endres2004a}
    
        \nocitepublications{ref:krysl2005a}
    
        \nocitepublications{ref:endres2007a}
    
        \nocitepublications{ref:endres2007b}
    
        \nocitepublications{ref:schwefe2014a}
    
        \nocitepublications{ref:endres2015a}
    
	\bibliographystylepublications{leplain}
	\bibliographypublications{le}
	
	\catagory{Patents}
	
        \nocitepatents{ref:endres2013a}
    
        \nocitepatents{ref:endres2013b}
    
        \nocitepatents{ref:prevost2013a}
    
        \nocitepatents{ref:hohl2015a}
    
	\bibliographystylepatents{leplain}
	\bibliographypatents{le}

    \catagory{Other Skills}
	
    \begin{bulletedlist}
		
        \item Engineering and Research: Design of Laboratory Experiments,
                        Stability Analysis,
                        Signal Processing,
                        Algorithm Design,
                        FEA,
                        Plasticity,
                        and Structural Engineer.
                        
        \item Programming: C,
                        C++,
                        C\#,
                        .NET Framework,
                        Visual Basic,
                        Fortran,
                        AutoLISP,
                        threading (POSIX and .NET),
                        XML,
                        XPath,
                        XSLT,
                        HTML,
                        XHTML,
                        CSS,
                        Windows Installer XML (WiX),
                        INT's WellLog graphing library,
                        UML,
                        XML Schema Definitions (XSD),
                        PHP,
                        JavaScript,
                        code profiling,
                        and software architecture.
                        
        \item Microsoft software: Windows,
                        Word,
                        Excel,
                        PowerPoint,
                        Project,
                        Access,
                        and Outlook.
                        
        \item Other software: Visual Studio,
                        AutoCAD,
                        Matlab,
                        TortoiseSVN/CVS,
                        GitHub,
                        SAP 2000,
                        RISA-3D,
                        iSIGHT,
                        LaTeX,
                        and NX.
                        
        \item Other: Computer trouble shooting and repair (hardware and software),
                        Basic electronics,
                        Embedded programming,
                        and Soldering.
                        
	\end{bulletedlist}
	

		\catagory{Certi{f}ications}
		
			\catentrycertification{1999}
                {Engineer in Training (E.I.T./F.E. Exam)}
                {Detroit, MI}
        

		\catagory{Af{f}iliations}
		
                \catentrymembership
        {2008}
        {Society of Petroleum Engineers}
    {PetroWiki moderator for \emph{Dynamics and Vibrations}.}
            

        \end{document}
    